---
title: "Business Intelligence Project"
author: "<Specify your name here>"
date: "<Specify the date when you submitted the lab>"
output:
  github_document: 
    toc: yes
    toc_depth: 4
    fig_width: 6
    fig_height: 4
    df_print: default
editor_options:
  chunk_output_type: console
---

# Student Details

|                                              |        |
|----------------------------------------------|--------|
| **Student ID Number**                        | 134782, 134783, 135232, 122998 |
| **Student Name**                             | Yasmin Choma, Moses Mbugua, Sadiki Hamisi,Glenn Oloo  |
| **BBIT 4.2 Group**                           | Group A    |
| **BI Project Group Name/ID (if applicable)** | Starfield    |

# Setup Chunk

**Note:** the following KnitR options have been set as the global defaults: <BR> `knitr::opts_chunk$set(echo = TRUE, warning = FALSE, eval = TRUE, collapse = FALSE, tidy = TRUE)`.

More KnitR options are documented here <https://bookdown.org/yihui/rmarkdown-cookbook/chunk-options.html> and here <https://yihui.org/knitr/options/>.

```{r setup, include=FALSE}
library(formatR)
knitr::opts_chunk$set(
  warning = FALSE,
  collapse = FALSE
)
```

# Understanding the Dataset (Exploratory Data Analysis (EDA))

## Loading the Dataset

### Source:

The dataset that was used can be downloaded here: *\<provide a link\>*

### Reference:

*\<Cite the dataset here using APA\>\
Refer to the APA 7th edition manual for rules on how to cite datasets: <https://apastyle.apa.org/style-grammar-guidelines/references/examples/data-set-references>*

# **DATASET 1: Pima Indians Diabetes - Data Summary and Preprocessing**

```{r}
if (!is.element("mlbench", installed.packages()[, 1])) {
  install.packages("mlbench", dependencies = TRUE)
}
require("mlbench")

data("PimaIndiansDiabetes")
summary(PimaIndiansDiabetes)
```

# **Exploring the Dataset Structure**

```{r}
str(PimaIndiansDiabetes)
```

\#**Data Preprocessing: Splitting the Dataset**

```{r}
library(caret)

train_index <- createDataPartition(PimaIndiansDiabetes$diabetes,
                                   p = 0.75,
                                   list = FALSE)
Pima_Indians_Diabetes_dataset_train <- PimaIndiansDiabetes[train_index, ]
Pima_Indians_Diabetes_dataset_test <- PimaIndiansDiabetes[-train_index, ]

```

# **Utilizing the naiveBayes() Function in the "e1071" Package**

```{r}
Pima_Indians_Diabetes_dataset_model_nb_e1071 <- # nolint
  e1071::naiveBayes(diabetes ~ pregnant + glucose + pressure + triceps + insulin + mass +
                      pedigree + age,
                    data = Pima_Indians_Diabetes_dataset_train)
```

# **Testing the Trained Model on the Testing Dataset**

```{r}
predictions_nb_e1071 <-
  predict(Pima_Indians_Diabetes_dataset_model_nb_e1071,
          Pima_Indians_Diabetes_dataset_test[, c("pregnant", "glucose", "pressure", "triceps",
                                     "insulin", "mass", "pedigree",
                                     "age"
                                     )])
```

# **Examining the Model Results**

```{r}
print(predictions_nb_e1071)
caret::confusionMatrix(predictions_nb_e1071,
                       Pima_Indians_Diabetes_dataset_test[,c("pregnant", "glucose", "pressure", "triceps",
                                                             "insulin", "mass", "pedigree",
                                                             "age", "diabetes")]$diabetes)

plot(table(predictions_nb_e1071,
           Pima_Indians_Diabetes_dataset_test[,c ("pregnant", "glucose", "pressure", "triceps",
                                                 "insulin", "mass", "pedigree",
                                                 "age", "diabetes")]$diabetes))

```
